Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-05-22 tex/paper1/paper1.tex
edits to the T_SSE

However, even this approach to identifying oscillatory power is not
quite complete, as it simply rejects the null hypothesis that the
\PS\ can be adequately explained by a red-noise power
spectrum.  Model comparison techniques similar to that described in
Section \ref{sec:anal} are required to prefer a model with oscillatory
content over one without. The difficulty in finding narrow-band
features in Fourier power spectra against a red-noise background power
spectrum has been recognized by \cite{2010MNRAS.402..307V} in the
study of XMM-Newton observations of highly variable Seyfert 1
galaxies.  \cite{2010MNRAS.402..307V} presents a model fitting and
comparison technique that is directly applicable to the search for
oscillatory power in coronal time-series.

@@

The discussion of Section \ref{ssec:corseis} shows that red-noise
power spectra has a powerful effect on the claims of a detection of
narrow-frequency band oscillations in single time-series.  When
looking at extended regions of coronal imaging data, evidence for the
presence of a {\it wave} in the corona is strengthened if it can be
shown that narrow frequency-band oscillations occur significantly
above the background signal in several neighboring pixels.  Spatial
extent is one key feature to claim of a detected wave.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This has implications for
the design of automated oscillation detection algorithms.  Such an
algorithm must take into account the nature of the \PS.
The power-law \PS\ itself lacks an easily definable
time-scale at or below which a background trend can be defined.
Automated detection algorithms that rely on background trend
subtraction such as \cite{2010SoPh..264..403I} must therefore look to
other reasons for to justify a time-scale.

>>>>

However, even this approach to identifying oscillatory power is not
quite complete, as it simply rejects the null hypothesis that the
\PS\ can be adequately explained by a red-noise power
spectrum.

Model comparison techniques similar to that described in
Section \ref{sec:anal} are required to prefer a model with oscillatory
content over one without. The difficulty in finding narrow-band
features in Fourier power spectra against a red-noise background power
spectrum has been recognized by \cite{2010MNRAS.402..307V} in the
study of XMM-Newton observations of highly variable Seyfert 1
galaxies.  \cite{2010MNRAS.402..307V} presents a model fitting and
comparison technique that is directly applicable to the search for
oscillatory power in coronal time-series.

@@

The discussion of Section \ref{ssec:corseis} shows that red-noise
power spectra has a powerful effect on the claims of a detection of
narrow-frequency band oscillations in single time-series.  When
looking at extended regions of coronal imaging data, evidence for the
presence of a {\it wave} in the corona is strengthened if it can be
shown that narrow frequency-band oscillations occur significantly
above the background signal in several neighboring pixels.  Spatial
extent is the key feature to claim of a detected wave.  Coronal
seismology derives its observational evidence from such detections,
and automated detection algorithms hold out the hope of greatly
increasing the number of oscillating regions detected.

Figure \ref{fig:compare171193} shows that time series from individual
pixels have power-law like power spectra.  This has implications for
the design of automated oscillation detection algorithms.  Such an
algorithm must take into account the nature of the \PS.  The power-law
\PS\ itself lacks an easily definable time-scale at or below which a
background trend can be defined.  Automated detection algorithms that
rely on background trend subtraction, such as
\cite{2010SoPh..264..403I} must therefore look to other reasons for to
justify a time-scale.
